Value Ordering, Discrepancies, and Restarts in Subgraph Solvers: \\ Some Half-Baked Mucking Around

### 2017-10-04 paper/paper.tex
Thingies

\definecolor{magma8}{rgb}{0.996078, 0.760784, 0.529412}

@@

\newcommand{\siplabel}[1]{\label{line:sip:#1}}
\newcommand{\siplineref}[1]{line~\ref{line:sip:#1}}
\begin{algorithm}[p]\DontPrintSemicolon\small\SetInd{0.1em}{1em}
    \begin{tikzpicture}[remember picture,overlay]
        \coordinate (restart1sc) at ($(pic cs:restart1s) + (0, 0.15)$);
        \coordinate (restart1ec) at ($(pic cs:restart1e) + (0, 0.00)$);
        \node [fill=magma8, rounded corners, fit=(restart1sc) (restart1ec)] { };
        \coordinate (restart2sc) at ($(pic cs:restart2s) + (0, 0.15)$);
        \coordinate (restart2ec) at ($(pic cs:restart2e) + (0, 0.00)$);
        \node [fill=magma8, rounded corners, fit=(restart2sc) (restart2ec)] { };
        \coordinate (restart3sc) at ($(pic cs:restart3s) + (0, 0.15)$);
        \coordinate (restart3ec) at ($(pic cs:restart3e) + (0, 0.00)$);
        \node [fill=magma8, rounded corners, fit=(restart3sc) (restart3ec)] { };
        \coordinate (restart4sc) at ($(pic cs:restart4s) + (0, 0.15)$);
        \coordinate (restart4ec) at ($(pic cs:restart4e) + (0, 0.00)$);
        \node [fill=magma8, rounded corners, fit=(restart4sc) (restart4ec)] { };
        \coordinate (restart5sc) at ($(pic cs:restart5s) + (0, 0.15)$);
        \coordinate (restart5ec) at ($(pic cs:restart5e) - (0, 0.10)$);
        \coordinate (restart5rc) at ($(pic cs:restart5r) + (0, 0.00)$);
        \node [fill=magma8, rounded corners, fit=(restart5sc) (restart5ec) (restart5rc)] { };
        \coordinate (restart6sc) at ($(pic cs:restart6s) + (0, 0.15)$);
        \coordinate (restart6ec) at ($(pic cs:restart6e) + (0, 0.00)$);
        \node [fill=magma8, rounded corners, fit=(restart6sc) (restart6ec)] { };
        \coordinate (restart7sc) at ($(pic cs:restart7s) + (0, 0.15)$);
        \coordinate (restart7ec) at ($(pic cs:restart7e) + (0, 0.00)$);
        \node [fill=magma8, rounded corners, fit=(restart7sc) (restart7ec)] { };
        \coordinate (restart8sc) at ($(pic cs:restart8s) + (0.05, 0.15)$);
        \coordinate (restart8ec) at ($(pic cs:restart8e) + (0, 0.00)$);
        \node [fill=magma8, rounded corners, fit=(restart8sc) (restart8ec)] { };
        \coordinate (restart9sc) at ($(pic cs:restart9s) + (0, 0.15)$);
        \coordinate (restart9ec) at ($(pic cs:restart9e) + (-0.15, 0.00)$);
        \node [fill=magma8, rounded corners, fit=(restart9sc) (restart9ec)] { };
    \end{tikzpicture}

@@

?? Also talk about position-biased

The performance of the degree-biased and degree heuristics is very similar: the degree-biased heuristic has
slightly worse performance below a 100s timeout, and effectively equal performance above it. This
shows that we can introduce an element of randomness into the degree value-ordering heuristic
without adversely affecting its performance \emph{in aggregate}. \Cref{figure:scatter-heuristics}
gives a more detailed look at these results. In this plot, satisfiable and unsatisfiable instances
are shown using dots and crosses respectively. On the $x$-axis we measure the degree heuristic,
whilst on the $y$-axis we measure random + restarts. Points on the outer axes represent instances
which timed out with one heuristic but not the other. This plot shows that on a case by case basis,
randomness can make a large difference to individual satisfiable instances.

@@

    \caption{Cumulative number of instances solved over time, with and without restarts.}
    \label{figure:restarts}
\end{figure}

@@

\Cref{figure:restarts} shows that either biased heuristic together with restarts is better
still---that is, if we are introducing restarts, then it is better to add a small amount of
randomness to a tailored deterministic heuristic than it is to throw away the heuristic altogether.
The degree-biased heuristics is stronger than position-biased, showing that exploiting ties and
relative sizes in the heuristic ordering is also worthwhile.

@@

?? maybe some engineering aspects: look at performance with restarts on degree, and at restarts
without nogood recording

>>>>

\definecolor{inferno9}{rgb}{0.992157, 0.929412, 0.501961}

@@

\newcommand{\siplabel}[1]{\label{line:sip:#1}}
\newcommand{\siplineref}[1]{line~\ref{line:sip:#1}}
\begin{algorithm}[p]\DontPrintSemicolon\small\SetInd{0.1em}{1em}
    \begin{tikzpicture}[remember picture,overlay]
        \coordinate (restart1sc) at ($(pic cs:restart1s) + (0, 0.15)$);
        \coordinate (restart1ec) at ($(pic cs:restart1e) + (0, 0.00)$);
        \node [fill=inferno9, rounded corners, fit=(restart1sc) (restart1ec)] { };
        \coordinate (restart2sc) at ($(pic cs:restart2s) + (0, 0.15)$);
        \coordinate (restart2ec) at ($(pic cs:restart2e) + (0, 0.00)$);
        \node [fill=inferno9, rounded corners, fit=(restart2sc) (restart2ec)] { };
        \coordinate (restart3sc) at ($(pic cs:restart3s) + (0, 0.15)$);
        \coordinate (restart3ec) at ($(pic cs:restart3e) + (0, 0.00)$);
        \node [fill=inferno9, rounded corners, fit=(restart3sc) (restart3ec)] { };
        \coordinate (restart4sc) at ($(pic cs:restart4s) + (0, 0.15)$);
        \coordinate (restart4ec) at ($(pic cs:restart4e) + (0, 0.00)$);
        \node [fill=inferno9, rounded corners, fit=(restart4sc) (restart4ec)] { };
        \coordinate (restart5sc) at ($(pic cs:restart5s) + (0, 0.15)$);
        \coordinate (restart5ec) at ($(pic cs:restart5e) - (0, 0.10)$);
        \coordinate (restart5rc) at ($(pic cs:restart5r) + (0, 0.00)$);
        \node [fill=inferno9, rounded corners, fit=(restart5sc) (restart5ec) (restart5rc)] { };
        \coordinate (restart6sc) at ($(pic cs:restart6s) + (0, 0.15)$);
        \coordinate (restart6ec) at ($(pic cs:restart6e) + (0, 0.00)$);
        \node [fill=inferno9, rounded corners, fit=(restart6sc) (restart6ec)] { };
        \coordinate (restart7sc) at ($(pic cs:restart7s) + (0, 0.15)$);
        \coordinate (restart7ec) at ($(pic cs:restart7e) + (0, 0.00)$);
        \node [fill=inferno9, rounded corners, fit=(restart7sc) (restart7ec)] { };
        \coordinate (restart8sc) at ($(pic cs:restart8s) + (0.05, 0.15)$);
        \coordinate (restart8ec) at ($(pic cs:restart8e) + (0, 0.00)$);
        \node [fill=inferno9, rounded corners, fit=(restart8sc) (restart8ec)] { };
        \coordinate (restart9sc) at ($(pic cs:restart9s) + (0, 0.15)$);
        \coordinate (restart9ec) at ($(pic cs:restart9e) + (-0.15, 0.00)$);
        \node [fill=inferno9, rounded corners, fit=(restart9sc) (restart9ec)] { };
    \end{tikzpicture}

@@

The performance of both the biased heuristics and the degree heuristic are very similar: the
degree-biased heuristic has slightly worse performance below a 100s timeout, and effectively equal
performance above it. This shows that we can introduce an element of randomness into the degree
value-ordering heuristic without adversely affecting its performance \emph{in aggregate}.
\Cref{figure:scatter-heuristics} gives a more detailed look at these results. In this plot,
satisfiable and unsatisfiable instances are shown using dots and crosses respectively. On the
$x$-axis we measure the degree heuristic, whilst on the $y$-axis we measure random + restarts.
Points on the outer axes represent instances which timed out with one heuristic but not the other.
This plot shows that on a case by case basis, randomness can make a large difference to individual
satisfiable instances.

@@

    \caption{Cumulative number of instances solved over time, with (dotted lines) and without (solid
    lines) restarts.}
    \label{figure:restarts}
\end{figure}

@@

\Cref{figure:restarts} shows that either biased heuristic together with restarts is better
still---that is, if we are introducing restarts, then it is better to add a small amount of
randomness to a tailored deterministic heuristic than it is to throw away the heuristic altogether.
The degree-biased heuristic is also stronger than position-biased, showing that exploiting ties and
relative sizes in the heuristic ordering is also worthwhile. Interestingly, the gap between degree-
and position-based is much larger when using restarts than it is when not using them.

@@

?? maybe some engineering aspects: look at performance with restarts on degree, and at restarts
without nogood recording, and what happens without nogoods in \cref{figure:scatter-nogoods}.

\begin{figure}[tb]
    \centering
    \includegraphics*{gen-graph-scatter-nogoods.pdf}

    \caption{Is nogood recording important?}
    \label{figure:scatter-nogoods}
\end{figure}

\begin{figure}[tb]
    \centering
    \includegraphics*{gen-graph-scatter-overheads.pdf}

    \caption{Is nogood recording and restarting expensive?}
    \label{figure:scatter-overhead}
\end{figure}
